---
title: "Statistical report of *`r name`*"
author: "Sivarajan Karunanithi"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

This report provides the basic statistical analysis of **`r name`**. It consists of various single category plots detailing on the distribution of read length, strand, and base modification. It also contains double category plots showing the combinations of aforementioned.

```{r echo=FALSE}
COSMO = theme_bw() + theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5), axis.title.x = element_text(size = 16, face = "bold"), axis.title.y = element_text(size = 16, face = "bold"), axis.text.x = element_text(size = 14, face = "bold"), axis.text.y = element_text(size = 14,face = "bold"), legend.title = element_text(size = 14, face = "bold"), legend.text = element_text(size = 14, face = "bold"))
```

**Total reads aligned to `r name` : `r aligned`**

###### Note: If graphs under some category are absent, it means there is not sufficient data with respect to that category. {#top}

### Read alignment percentage of various read lengths

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#read-alignment-percentage-of-various-read-lengths" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  try(print(ggplot(melt(table(subtt$V2)/aligned*100), aes(x=Var1, y=value))+geom_bar(stat = "identity")+xlab("Read Length")+ylab("% of aligned reads") + COSMO))
```

### Alignment percentage of reads with (Un)Modified bases

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#alignment-percentage-of-reads-with-unmodified-bases" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  try(print(ggplot(melt(table(subtt$V3)/aligned*100), aes(x=Var1, y=value))+geom_bar(stat = "identity")+xlab("Modified?")+ylab("% of aligned reads")+COSMO))
```

### Strand specific alignment percentage of reads

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#strand-specific-alignment-percentage-of-reads" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  try(print(ggplot(melt(table(subtt$V4)/aligned*100), aes(x=Var1, y=value))+geom_bar(stat = "identity")+xlab("Strand")+ylab("% of aligned reads") + COSMO))

  tab=table(subset(tt,V1==name & V5 != "-")$V5)
  aligned=nrow(subset(tt,V1==name))

  if(length(tab) >0){
    threshold=nrow(subset(tt,V1==name & V5 != "-"))*0.05
    threshold=max(threshold,1)
  }  else {
    threshold=0
  }
```

### Reads aligned with base modifications above `r threshold` reads

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#reads-aligned-with-base-modifications-above-n-reads" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  tab=table(subset(tt,V1==name & V5 != "-")$V5)
  aligned=nrow(subset(tt,V1==name))

  if(length(tab) >0){
    threshold=nrow(subset(tt,V1==name & V5 != "-"))*0.05
    threshold=max(threshold,1)
    
    if(nrow(melt(tab[tab>=threshold]))>1){
      try(print(ggplot(melt(tab[tab>=threshold]), aes(x=Var1, y=value))+geom_bar(stat = "identity")+xlab("Base")+ylab("Count") + COSMO))
		}
	}


```

### Alignment percentage of reads with base modifications above `r threshold` reads

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#alignment-percentage-of-reads-with-base-modifications-above-n-reads" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  tab=table(subset(tt,V1==name & V5 != "-")$V5)
  aligned=nrow(subset(tt,V1==name))

  if(length(tab) >0){
    threshold=nrow(subset(tt,V1==name & V5 != "-"))*0.05
    threshold=max(threshold,1)
    
    if(nrow(melt(tab[tab>=threshold]))>1){
      try(print(ggplot(melt(tab[tab>=threshold]/aligned*100), aes(x=Var1, y=value))+geom_bar(stat = "identity")+xlab("Base")+ ylab("% of reads aligned") + COSMO))
		}
	}
```

### Strand specific reads of varied length

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#strand-specific-reads-of-varied-length" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  #double category plots
  try(print(ggplot(melt(table(subtt$V4,subtt$V2)), aes(x=Var2, y=value, fill=Var1))+geom_bar(stat = "identity")+xlab("Read Length")+ylab("Count") + guides(fill=guide_legend(title="Strand")) + COSMO))

```

### Modification status specific reads of varied length

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#modification-status-specific-reads-of-varied-length" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  try(print(ggplot(melt(table(subtt$V3,subtt$V2)), aes(x=Var2, y=value, fill=Var1))+geom_bar(stat = "identity")+xlab("Read Length")+ylab("Count") + guides(fill=guide_legend(title="Modified?")) + COSMO))

```

### 1-base modification specific reads of varied length

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#1-base-modification-specific-reads-of-varied-length" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  tab=table(subset(tt,V1==name & V5 != "-")$V5)
  aligned=nrow(subset(tt,V1==name))
  if(length(tab) >0){
    #Subset with 1-base modifications
      modtt=subset(subtt,V5 %in% c("A","C","G","T"))
      if(nrow(modtt) >0){
        try(print(ggplot(melt(table(modtt$V5,modtt$V2)), aes(x=Var2, y=value, fill=Var1))+geom_bar(stat = "identity")+xlab("Read Length")+ylab("Count") + guides(fill=guide_legend(title="Base")) + COSMO))
      }
    }
```

### Strand specific reads with respect to base modification status

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#strand-specific-reads-with-respect-to-base-modification-status" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  try(print(ggplot(melt(table(subtt$V3,subtt$V4)), aes(x=Var2, y=value, fill=Var1))+geom_bar(stat = "identity")+xlab("Strand")+ylab("Count") + guides(fill=guide_legend(title="Modified?")) + COSMO))
```

### Strand specific coverage plot

<a href="https://github.com/SchulzLab/RAPID/blob/master/PlotInfo.md#strand-specific-coverage-plot" target="_blank">See Help</a>  &nbsp; [Back To Top](#top)

```{r echo=FALSE}
  idx=which(annotations$label==name)
  a=poscov[poscov$region==name,]
  b=negcov[negcov$region==name,]  
  a$region=NULL
  b$region=NULL
  
  pstn=c()
  for(ind in idx) {
    regStart=as.numeric(annotations$start[ind])
    regEnd=as.numeric(annotations$end[ind])
    if(regStart%%2==0) { 
      pstn=c(pstn,(regStart+1):regEnd)
    } else {
      pstn=c(pstn,regStart:(regEnd-1))
    }
  }
  a$position=pstn
  b$position=pstn
  b$depth= b$depth*-1
  
  try(print(ggplot(a, aes(position,depth)) + ylim(range(c(b$depth,a$depth))) + 
    geom_bar(stat="identity", aes(fill="+")) + 
    geom_bar(aes(b$position, b$depth, fill="-"), stat="identity") + 
    guides(fill=guide_legend(title="Strand")) +
    labs(x="Position", y="Coverage", title="") + COSMO))
```

This document was created with R Markdown and the Knit package. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see http://rmarkdown.rstudio.com.